A re-examination of the role of friction in the original Social Force Model

### 2019-06-21 paper.tex
correcciones parrafos turbios de intro

\textcolor{red}{More recent measures of the fundamental diagram in an extremely dense
 situation show that, sometimes, the flux may increase with the density (Ref.~\cite{lohner1}). 
This seems to contradict the results of Ref.~\cite{helbing3}. But both results seem 
not to be completely  comparable since data was acquired at different points, and thus,
at different stages of the ritual. Ref.~\cite{lohner1}, indeed, stated that the fundamental 
diagram may strongly depend on the type of motion and the nature of the event.}\\

\textcolor{red}{A lot of research has been done using data from the Mecca pilgrimage.
Although in this work we focused on Ref.~\cite{helbing3}. There were several investigations 
using real data to calibrate parameters of the PedFlow model developed by 
L\"ohner et al. Ref.~\cite{lohner2}. Recently a paper was published that uses 
the Kalman filter ensemble to adjust the parameters of this model Ref.~\cite{Togashi1}. 
For more information on PedFlow and Mecca pilgrimage measurements
see Refs.~\cite{Boltes,Dridi1,Dridi2,Baqui1,lohner1} }\\

@@

\textcolor{red}{Our starting point is the re-examination of the (basic) SFM. 
We propose a reduce-in-units equation of motion of the SFM. In this new picture,
the social force $\mathbf{f}_s$ depends on an intensity $\mathcal{A}$, the granular
force $\mathbf{f}_g$ depends on $\mathcal{K}$, and the desired force $\mathbf{f}_d$
only depends on the target. In Section~\ref{appendix_1} we derivate this 
reduce-in-units equation of motion and its corresponding control parameters ($\mathcal{A}$ and $\mathcal{K}$). }\\

>>>>

\textcolor{red}{More recent findings on the fundamental diagram for an extremely dense
 situation show that, sometimes, the flux may increase with the density (see Ref.\cite{lohner1}). 
This seems to contradict the results of Ref.~\cite{helbing3}. But both results appear 
not to be completely  comparable since data was acquired at different points, and thus,
at different stages of the ritual. Ref.~\cite{lohner1}, indeed, states that the fundamental 
diagram may strongly depend on the type of motion and the nature of the event.}\\

\textcolor{red}{ Our work focuses on data from Ref.~\cite{helbing3}. 
Further measurements can be found in Refs.~\cite{Boltes,Dridi1,Dridi2,Baqui1,lohner1}.
The PedFlow model developed by L\"ohner et al. Ref.~\cite{lohner2}  
is an alternative to the Helbing model. Togashi et al.  Ref.~\cite{Togashi1} 
improved the calibration of this model using a Kalman filter ensemble. }\\

@@

\textcolor{red}{Our starting point will be the re-examination of the (basic) SFM. 
We propose a reduce-in-units equation of motion of the SFM (see Section~\ref{appendix_1} 
for details). From this point of view, the parameter $A$ standing for the intensity of the
 social force $\mathbf{f}_s$ is replaced by the reduced-in-units parameter $\mathcal{A}$.
 The friction intensity $\kappa$ of the granular force $\mathbf{f}_g$ is replaced by the reduced-in-units
 parameter $\mathcal{K}$. No other parameters are required in the reduced-in-units model
 since $m$, $v_d$, $\tau$ and $B$ are all included in $\mathcal{A}$ and $\mathcal{K}$.
 The desired force $\mathbf{f}_d$, indeed, will only depend on the target direction. In Section~\ref{appendix_1} we derivate the 
reduce-in-units equation of motion and the meaning of the control parameters ($\mathcal{A}$ and $\mathcal{K}$). }\\
